---
title: "Code Assignment 1"
author: "Team 5"
date: "Due: 2021-09-29 23:59"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---
# Case Study {.tabset .tabset-pills}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(readxl)
library(tidyverse)
library(gt)
library(gtsummary)
library(plotly)
library(readxl)
library(corrplot)
library("gridExtra")
library("ggplot2")
library(ggpubr)
library(dplyr)
library(car)
library(jtools)
```
A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report. 

*For this assignment, ignore the categorical variables (gender, smoker, cities)*

## Question 1 {.tabset .tabset-pills}

Perform univariate analyses on the quantitative variables (center, shape, spread). Include descriptive statistics, and histograms. Be sure to use terms discussed in class such as bimodal, skewed left, etc.

### Inspect, and Clean the Data 
```{r dataset, include=FALSE}
Insurance <- read_excel("../Data/insurance_0126_Group5.xlsx",
                             col_types = c("numeric", "numeric","numeric","numeric", "numeric","numeric","numeric", "numeric","numeric"))
```

First, we should inspect the data to determine if all variables within the data set to ensure they make sense. The below output of observations and variables indicate that there are categorical and Quantitative variables. 

```{r, echo=FALSE}
str(Insurance)
```

Below is the below code chunk will be removing the categorical data from summaries for our analysis. 

```{r}
Insurance$Female <- NULL 
Insurance$WinterPark <- NULL
Insurance$WinterSprings <- NULL
Insurance$Oviedo <- NULL
Insurance$Smoker <- NULL
```

### Center (Mean, Median)

```{r, echo=FALSE}
Insurance %>%
tbl_summary(statistic = list(all_continuous() ~ c("{mean} ({sd})",
"{median} ({p25}, {p75})",
"{min}, {max}"),
all_categorical() ~ "{n} / {N} ({p}%)"),
type = all_continuous() ~ "continuous2"
)
```

### Center (Mode) & Shape {.tabset .tabset-pills}

#### Distribution of Primary Beneficiary Age
The below output is the mode for Primary Beneficiary Age

```{r, echo=FALSE}

getModesAge <- function(x) {
  ux <- unique(x)
  tab <- tabulate(match(x, ux))
  ux[tab == max(tab)]
}
getModesAge(Insurance$Age)

```

```{r, echo=FALSE}
ggp1 <- ggplot(Insurance, aes(Age)) +         
  geom_histogram(aes(y = ..density..), binwidth = 2 , col = 'black', fill = 'MidnightBlue', alpha = 0.75, bins = 45)+
  geom_density(color = "#000000", fill = "#FAF0E6", alpha = 0.4)+
  labs(x = 'Age', y= NULL) 

text1 <- paste("Text regarding age goes here break up sentences to make pretty")
text.a <- ggparagraph(text = text1, face = "italic", size = 8, color = "black")

ggarrange(ggp1, text.a, ncol = 1, nrow =2 )

```

#### Distribution of Primary Beneficiary BMI
The below output is the mode for Primary Beneficiary BMI
```{r, echo=FALSE}
getModesBMI <- function(x) {
  ux <- unique(x)
  tab <- tabulate(match(x, ux))
  ux[tab == max(tab)]
}
getModesBMI(Insurance$BMI)

```

```{r, echo=FALSE}
ggp2 <- ggplot(Insurance, aes(BMI)) +  
  geom_histogram(aes(y = ..density..), binwidth = 2,col = 'black', fill = 'CadetBlue', alpha = 0.75, bins = 45)+
  geom_density(color = "#000000", fill = "#FAF0E6", alpha = 0.5)+
  labs(x = 'BMI', y= NULL)

text2 <- paste("Text regarding BMI here break up to make pretty")
text.b <- ggparagraph(text = text2, face = "italic", size = 8, color = "black")

ggarrange(ggp2, text.b, ncol = 1, nrow =2 )
```

#### Distribution of Dependents
The below output is the mode for Dependents per Insurance Policy
```{r, echo=FALSE}
getModesChildren <- function(x) {
  ux <- unique(x)
  tab <- tabulate(match(x, ux))
  ux[tab == max(tab)]
}
getModesChildren(Insurance$Children)

```

```{r, echo=FALSE}
ggp3 <- ggplot(Insurance, aes(Children)) +  
  geom_histogram(aes(y = ..density..), binwidth = 0.5,col = 'black', fill = 'SeaGreen', alpha = 0.75, bins = 7)+
  geom_density(color = "#000000", fill = "#FAF0E6", alpha = 0.5)+
  labs(x = 'Children', y= NULL)

text3 <- paste("Text regarding children here break up to make pretty")
text.c <- ggparagraph(text = text3, face = "italic", size = 8, color = "black")

ggarrange(ggp3, text.c, ncol = 1, nrow =2 )
```

### Spread {.tabset .tabset-pills}

#### Spead of Age 
```{r, echo=FALSE}
boxplot(Insurance$Age, main="Figure 1.4", xlab="Spread of Age", ylab="Years", col="Blue")
```

#### Spread of BMI 
```{r, echo=FALSE}
boxplot(Insurance$BMI, main="Figure 1.5", xlab="Spread of BMI", ylab="Body Mass Index", col="Red")
```

#### Spread of Children
```{r, echo=FALSE}
boxplot(Insurance$Children, main="Figure 1.6", xlab="Spread of Children", ylab="Number of Dependents",  col="Green")
```


## Question 2 {.tabset .tabset-pills}

Perform bivariate analyses on the quantitative variables (direction, strength and form). Describe the linear association between all variables. 


Quantitative Variable Correlations:

### Relationship 
Age - Charges | The strongest positive correlation is between the age of customers and their charges. As per their correlation relationship, which is 0.411474, states that this is a positive and moderate correlation. The grouping within the scatterplot confirms this.
```{r, echo=FALSE}
cor(Insurance$Charges, Insurance$Age)
```
BMI - Charges | The correlation between BMI and Charges is positive but weak at 0.1395063. The grouping is sporadic but does follow a slight grouping pattern.

```{r, echo=FALSE}
cor(Insurance$Charges, Insurance$BMI)
```
Children - Charges | The correlation between the number of dependents and total annual charges is the weakest correlation. Albeit that it is positive the correlation is .0149766. After reviewing the grouping it almost suggests having less children is leading to higher annual charges but the population tends to be skewed towards
```{r, echo=FALSE}
cor(Insurance$Charges, Insurance$Children)
```


### Strength 
```{r, echo=FALSE}

reduced <- Insurance %>% 
  select(Charges,Age,BMI,Children)


corrplot(cor(reduced),
         main = "2.4 Correlation Plot",
         type = "lower",
         order = "hclust", 
         tl.col = "black",
         tl.srt = 45,
         addCoef.col = "black",
         diag = FALSE,
         mar=c(0,0,1,0))

```

### Form 
```{r, echo=FALSE}

plot(Insurance$Age, Insurance$Charges, main="2.1 Relationship of Age and Expenditures", xlab="Customer's Age", ylab="Total Medical Expenditures", col="Blue")
plot(Insurance$BMI, Insurance$Charges, main="2.2 Relationship of BMI and Expenditures", xlab="Customer's of Body Mass Index", ylab="Total Medical Expenditures", col="Red")
plot(Insurance$Children, Insurance$Charges, main="2.3 Relationship of Depenents and Expenditures", xlab="Number of Dependents", ylab="Total Medical Expenditures", col="Green")
```



## Question 3 {.tabset .tabset-pills}

Generate a regression equation in the following form:

                        $Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children$

### Regression Equation for Annual Medical Expenses

Based off our our model summary from the data provided our equation is as follows for annual charges; an intercept value of 
-$5,962.00 with a coefficient value for age set at $346.50, BMI at $133.00, and children at $107.30.
```{r, echo=FALSE}
 model <- lm(Charges ~ Age + BMI + Children, data = Insurance)
summ(model)
```
$$Charges = -5962.00 + 346.50(Age) + 133.00(BMI) - 107.30(Children)$$


## Question 4 {.tabset .tabset-pills}

An eager insurance representative comes back with a potential client. The client is 40, their BMI is 30, and they have one dependent. Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)

### New Prediction for Medical Expenses
```{r, echo=FALSE}
 newPrediction <- data.frame(Age = 40, BMI = 30, Children = 1)
predict (model, newdata = newPrediction, interval = "confidence", level = .95)
```

As per our regression equation, this Florida health insurance company can expect charges for this individual to annually be $11,782.35. However with a 95% confidence interval the lower bound of charges accumulated would be $8,598.57 to $14,966.13 annually.
