---
title: "Code Assignment 1"
author: "Team 5"
date: "Due: 2021-09-29 23:59"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---
# Case Study {.tabset .tabset-pills}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(readxl)
library(tidyverse)
library(gt)
library(gtsummary)
library(plotly)
library(readxl)
library(corrplot)
library("gridExtra")
library("ggplot2")
library(ggpubr)
library(dplyr)
library(car)
library(jtools)
```
A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report. 

*For this assignment, ignore the categorical variables (gender, smoker, cities)*

## Question 1 {.tabset .tabset-pills}

Perform univariate analyses on the quantitative variables (center, shape, spread). Include descriptive statistics, and histograms. Be sure to use terms discussed in class such as bimodal, skewed left, etc.

### Inspect, and Clean the Data 
```{r dataset, include=FALSE}
Insurance <- read_excel("../Data/insurance_0126_Group5.xlsx",
                             col_types = c("numeric", "numeric","numeric","numeric", "numeric","numeric","numeric", "numeric","numeric"))
```

First, we should inspect the data to determine which variables should be used within the data set. Below is the output of observations and variables which indicate that there are categorical and Quantitative variables. 
<br>
```{r, echo=FALSE}
str(Insurance)
```

For this assignment, we will ignore the categorical variables.  The code chunk below will remove gender, smoker, and cities from the data set. 
<br>
```{r}
Insurance$Female <- NULL 
Insurance$WinterPark <- NULL
Insurance$WinterSprings <- NULL
Insurance$Oviedo <- NULL
Insurance$Smoker <- NULL
```

### Center (Mean, Median)
The variables listed below were part of our analysis and are included in the following *Summary of Statistical Information*.

**Figure 1.1**
<br>
<br>
  1. **Charges**: Primary beneficiaries paid between $2,494 and $55,135. 

  2. **Age**: The data output confirms that the data for Age is skewed to the right as the Mean is larger than the Median.

  3. **BMI**: The data output for beneficiaries BMI is symmetrical as the Mean and Median are almost the same number. Identifying the mode will help validate this observation.

  4. **Children**: 34% of the primary beneficiaries did not have dependents.
<br>
<br>

```{r, echo=FALSE}
Insurance %>%
tbl_summary(statistic = list(all_continuous() ~ c("{mean} ({sd})",
"{median} ({p25}, {p75})",
"{min}, {max}"),
all_categorical() ~ "{n} / {N} ({p}%)"),
type = all_continuous() ~ "continuous2"
)
```

### Center (Mode) & Shape {.tabset .tabset-pills}

#### Distribution of Primary Beneficiary Age
The below output is the mode for Primary Beneficiary Age data. The output indicates that the data is bimodal which we can analyze further by creating a histogram graph. 

```{r, echo=FALSE}

getModesAge <- function(x) {
  ux <- unique(x)
  tab <- tabulate(match(x, ux))
  ux[tab == max(tab)]
}
getModesAge(Insurance$Age)

```
<br>
**Figure 1.2 : Histogram of Primary Beneficiary Age Distribution**
<br>
```{r, echo=FALSE, warning=FALSE}
ggp1 <- ggplot(Insurance, aes(Age)) +         
  geom_histogram(col = 'black', fill = 'MidnightBlue', alpha = 0.75, bins = 20, binwidth = 1)+
  labs(x = 'Age', y= NULL)

text1 <- paste("The above Histogram displays that the Primary Beneficiaries Age data is Symmetric bimodal distribution with two centers being at 27 and 45 years.")
text.a <- ggparagraph(text = text1, face = "italic", size = 12, color = "black")

ggarrange(ggp1, text.a, ncol = 1, nrow = 2 )
```

#### Distribution of Primary Beneficiary BMI
The below output is the mode for Primary Beneficiary BMI
```{r, echo=FALSE}
getModesBMI <- function(x) {
  ux <- unique(x)
  tab <- tabulate(match(x, ux))
  ux[tab == max(tab)]
}
getModesBMI(Insurance$BMI)

```
<br>
**Figure 1.3 : Histogram of Primary Beneficiary BMI Distribution**
<br>
```{r, echo=FALSE, warning=FALSE}
ggp2 <- ggplot(Insurance, aes(BMI)) +  
  geom_histogram(binwidth = 1,col = 'black', fill = 'CadetBlue', na.rm = TRUE, alpha = 0.75, bins = 50)+
  labs(x = 'BMI', y= NULL)+
  xlim(15, 45)

text2 <- paste("The above Histogram displays that the Primary Beneficiaries BMI data is Symmetrical Unimodal distribution with the center at 30.2")
text.b <- ggparagraph(text = text2, face = "italic", size = 12, color = "black")

ggarrange(ggp2, text.b, ncol = 1, nrow = 2 )
```

#### Distribution of Dependents
The below output is the mode for Dependents per Insurance Policy
```{r, echo=FALSE}
getModesChildren <- function(x) {
  ux <- unique(x)
  tab <- tabulate(match(x, ux))
  ux[tab == max(tab)]
}
getModesChildren(Insurance$Children)

```
<br>
**Figure 1.4 : Histogram of Distribution for Policy Dependents**
<br>
```{r, echo=FALSE, warning=FALSE}
ggp3 <- ggplot(Insurance, aes(Children)) +  
  geom_histogram(aes(y = ..density..), binwidth = 0.5,col = 'black', fill = 'SeaGreen', alpha = 0.75, bins = 50)+
  labs(x = 'Children', y= NULL)+
   xlim(-1, 6)

text3 <- paste("The above Histogram displays that the Primary Beneficiaries Dependents data is Right-Skewed distribution that is positively-skewed.")
text.c <- ggparagraph(text = text3, face = "italic", size = 12, color = "black")

ggarrange(ggp3, text.c, ncol = 1, nrow = 2 )
```

### Spread {.tabset .tabset-pills}

#### Spead of Age 

<br>

**Figure 1.5 : Spread of Age**

The boxplot shows us many details of the spread of the age.

  - Median is 40
  
  - Lower (1st) quartile is 30
  
  - Upper (3rd) quartile is 52
  
  - Maximum at 64
  
  - Minimum at 24
  
  - No outliers

```{r, echo=FALSE}
boxplot(Insurance$Age, xlab="Spread of Age", ylab="Years", col="Blue")
```

#### Spread of BMI

<br>

**Figure 1.6 : Spread of BMI**

The boxplot shows us many details of the spread of the BMI.

  - Median is about 28
  
  - Lower (1st) quartile is 25
  
  - Upper (3rd) quartile is 33
  
  - Maximum at 42
  
  - Minimum at 16
  
  - No outliers

```{r, echo=FALSE}
boxplot(Insurance$BMI, xlab="Spread of BMI", ylab="Body Mass Index", col="Red")
```

#### Spread of Children

<br>

**Figure 1.7 : Spread of Dependents**

The boxplot shows us many details of the spread of the Children.

  - Median is 1
  
  - Lower (1st) quartile is 0
  
  - Upper (3rd) quartile is 2
  
  - Maximum at 5
  
  - Minimum at 0
  
  - No outliers

```{r, echo=FALSE}
boxplot(Insurance$Children, xlab="Spread of Dependents", ylab="Number of Dependents",  col="Green")
```


## Question 2 {.tabset .tabset-pills}

Perform bivariate analyses on the quantitative variables (direction, strength and form). Describe the linear association between all variables. 


Quantitative Variable Correlations:

### Relationship 
Age - Charges | The strongest positive correlation is between the age of customers and their charges. As per their correlation relationship, which is 0.411474, states that this is a positive and moderate correlation. The grouping within the scatterplot confirms this.
```{r, echo=FALSE}
cor(Insurance$Charges, Insurance$Age)
```
BMI - Charges | The correlation between BMI and Charges is positive but weak at 0.1395063. The grouping is sporadic but does follow a slight grouping pattern.

```{r, echo=FALSE}
cor(Insurance$Charges, Insurance$BMI)
```
Children - Charges | The correlation between the number of dependents and total annual charges is the weakest correlation. Albeit that it is positive the correlation is .0149766. After reviewing the grouping it almost suggests having less children is leading to higher annual charges but the population tends to be skewed towards
```{r, echo=FALSE}
cor(Insurance$Charges, Insurance$Children)
```


### Strength
<br>
**Figure 2.1 : Correlation Plot**]

The below correlation plot displays that the strongest correlation is between Charges and the Primary Beneficiaries Age. 
```{r, echo=FALSE}

reduced <- Insurance %>% 
  select(Charges,Age,BMI,Children)


corrplot(cor(reduced),
         type = "lower",
         order = "hclust", 
         tl.col = "black",
         tl.srt = 45,
         addCoef.col = "black",
         diag = FALSE,
         mar=c(0,0,1,0))

```

### Form {.tabset .tabset-pills}

#### Age and Expenditures 
<br> 
There is a slightly strong positive association in the linear relationship between Medical expenditures and the customers age.
<br>
```{r, echo=FALSE}
plot(Insurance$Age, Insurance$Charges, main="2.2 Relationship of Age and Expenditures", xlab="Customer's Age", ylab="Total Medical Expenditures", col="Blue")
```

#### BMI and Expenditures
<br>
The linear relationship between medical expenses and BMI appear to have a weak positive association.
```{r, echo=FALSE}
plot(Insurance$BMI, Insurance$Charges, main="2.3 Relationship of BMI and Expenditures", xlab="Customer's of Body Mass Index", ylab="Total Medical Expenditures", col="Red")
```

#### Depenents and Expenditures
<br>
sample for 2.4
```{r, echo=FALSE}
plot(Insurance$Children, Insurance$Charges, main="2.4 Relationship of Depenents and Expenditures", xlab="Number of Dependents", ylab="Total Medical Expenditures", col="Green")
```



## Question 3 {.tabset .tabset-pills}

Generate a regression equation in the following form:

                        $Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children$

### Regression Equation for Annual Medical Expenses

Based off our our model summary from the data provided our equation is as follows for annual charges; an intercept value of 
-$5,962.00 with a coefficient value for age set at $346.50, BMI at $133.00, and children at $107.30.
```{r, echo=FALSE}
 model <- lm(Charges ~ Age + BMI + Children, data = Insurance)
summ(model)
```
$$Charges = -5962.00 + 346.50(Age) + 133.00(BMI) - 107.30(Children)$$


## Question 4 {.tabset .tabset-pills}

An eager insurance representative comes back with a potential client. The client is 40, their BMI is 30, and they have one dependent. Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)

### New Prediction for Medical Expenses
```{r, echo=FALSE}
 newPrediction <- data.frame(Age = 40, BMI = 30, Children = 1)
predict (model, newdata = newPrediction, interval = "confidence", level = .95)
```

As per our regression equation, this Florida health insurance company can expect charges for this individual to annually be $11,782.35. However with a 95% confidence interval the lower bound of charges accumulated would be $8,598.57 to $14,966.13 annually.
