---
title: "Coding Assignment 2"
author: "Team N"
date: "Due: 2021-10-23 23:59"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
#Put any packages you need here
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(tidyverse)
library(gt)
library(gtsummary)
library(plotly)
library(readxl)
library(corrplot)
library("gridExtra")
library("ggplot2")
library(ggpubr)
library(dplyr)
library(car)
library(jtools)
```

A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


```{r dataset, include=FALSE}
insurance <- read.csv("../Data/insurance_0126_Group5.csv")
```



## Question 1

Generate this regression equation:

$$Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children + \beta_{4}*Female + \beta_{5}*Smoker + \beta_{6}*WinterSprings + \beta_{7}*WinterPark + \beta_{8}*Oviedo$$


Based off our our model summary from the data provided our equation is as follows for annual charges; an intercept value of 
-$13,721.51 with a coefficient value for age set at $295.68, BMI at $392.64, children at $84.60, female at $1,489.17, smoker at $21,374.71, Winter Springs at -$1,419.77, Winter Park at -$4,358.32, and Oviedo at -$2,845.19.

```{r q1}
 model <- lm(Charges ~ Age + BMI + Children + Female + Smoker + WinterSprings + WinterPark + Oviedo, data = insurance)
summ(model)
```
$$Charges = -13,721.51 + 295.68(Age) + 392.64(BMI) + 84.60(Children) + 1,489.17(Female) + 21,374.71(Smoker) - 1,419.77(WinterSprings) - 4,358.32(WinterPark) - 2,845.19(Oviedo)$$

Which independent variables test significant in a two-tailed test? Use $\alpha = 0.2$



## Question 2

Interpret the coefficients of all the independent variables that tested significant.

Test their significance levels. Value of the larger coefficients is what matters.


## Question 3

The insurance agent returns with another client:

- Age: 35
- BMI: 26
- Children: 1
- Gender: Female
- Smoker: No
- City: Sanford

Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)

```{r q3, echo=FALSE}
 newPrediction <- data.frame(Age = 35, BMI = 26, Children = 1, Female = 1, Smoker = 0, WinterSprings = 0, WinterPark = 0, Oviedo = 0)
predict (model, newdata = newPrediction, interval = "confidence", level = .95)

```

As per our regression equation, this Florida health insurance company can expect charges for this individual to annually be $9,517.64. However with a 95% confidence interval the lower bound of charges accumulated would be $5,868.46 to $13,166.82 annually.

## Question 4

Compare the model from question 1, to a model that does not include the group of city dummies. Does including the cities reduce the SSE by a statistically significant amount? (check the partial F-test for significance of the dummies as a group). Use $\alpha = 0.05$

```{r q4}

```


