---
title: "Coding Assignment 2"
author: "Team 5: The Fanstatic Five"
date: "Due: 2021-10-23 23:59"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
#Put any packages you need here
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(tidyverse)
library(gt)
library(gtsummary)
library(plotly)
library(readxl)
library(corrplot)
library("gridExtra")
library("ggplot2")
library(ggpubr)
library(dplyr)
library(car)
library(jtools)
library(rstatix)
library(stats)
library(xtable)
library(knitr)
```

<font face = Helvetica size = 2 color = black > A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. <br> <br> The data on the 50 customers in the sample is as follows:<br>
-	Charges: Total medical expenses for a particular insurance plan (in dollars)<br> -	Age: Age of the primary beneficiary <br> -	BMI: Primary beneficiary’s body mass index (kg/m2) <br>-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female) <br>-	Children: Number of children covered by health insurance plan (includes other dependents as well) <br>-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker) <br>-	Cities: Dummy variables for each city with the default being Sanford <br> <br> Answer the following questions using complete sentences and attach all output, plots, etc. within this report.</font>

```{r dataset, include=FALSE}
insurance <- read.csv("../Data/insurance_0126_Group5.csv")
```
## Question 1

### Generating a Regression Equation
<font face = Helvetica size = 2 color = black >Generate this regression equation:<br> $$ \scriptsize Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children + \beta_{4}*Female + \beta_{5}*Smoker + \beta_{6}*WinterSprings + \beta_{7}*WinterPark + \beta_{8}*Oviedo$$</font>

---

<font face = Helvetica size = 2 color = DarkSlateBlue >Based off our our model summary from the data provided our equation is as follows for annual charges; an intercept value of 
-$13,721.51 with a coefficient value for Age set at $295.68, BMI at $392.64, Children at $84.60, Female at $1,489.17, Smoker at $21,374.71, Winter Springs at -$1,419.77, Winter Park at -$4,358.32, and Oviedo at -$2,845.19.</font>
<br>
```{r q1, echo=FALSE}
 model <- lm(Charges ~ Age + BMI + Children + Female + Smoker + WinterSprings + WinterPark + Oviedo, data = insurance)
summ(model)
```
<font face = Helvetica size = 3 color = DarkSlateBlue > Regression Equation </font>


**$$ \scriptsize Charges = -13,721.51 + 295.68(Age) + 392.64(BMI) + 84.60(Children) + 1,489.17(Female) + 21,374.71(Smoker) - 1,419.77(WinterSprings) - 4,358.32(WinterPark) - 2,845.19(Oviedo)$$**

### Two-Tailed Test 

<font face = Helvetica size = 2 color = black > Which independent variables test significant in a two-tailed test? Use $\alpha = 0.2$ </font>
<br>


---

``` {r q1.2, include=FALSE}
regsummary <- summary(model)

regsummary

```
<font face = Helvetica size = 2 color = DarkSlateBlue > The below results of a two-tailed test confirm that Age, BMI, Smoker, and WinterPark test significant at $\alpha = 0.2$ </font>

```{r q1.3, echo=FALSE}
mod_summary_sign <- regsummary$coefficients[ , 4]  # Pull out p-values
mod_summary_stars <- NA   
mod_summary_stars[mod_summary_sign < 0.2] <- "YES, Variable is Significant"
mod_summary_stars[mod_summary_sign > 0.2] <- "NO, Variable is Not Significant"
names(mod_summary_stars) <- names(mod_summary_sign)
kable(mod_summary_stars, format = "simple", col.names = "p < 0.20")
```
<br>
<br>

## Question 2

### Coefficient Analysis 

<font face = Helvetica size = 2 color = black > Interpret the coefficients of all the independent variables that tested significant. <br> Test their significance levels. Value of the larger coefficients is what matters.</font>
<br>

---

<font face = Helvetica size = 2 color = DarkSlateBlue > 
In order for an independent variable to test significant, the p-value must be smaller than the alpha value (confidence level).
In this question, the alpha value is 0.2 (80% confidence level).
The following independent variables test significant at an 80% confidence level:

- Age (p-value = 0.00)
- BMI (p-value = 0.04)
- Smoker (p-value = 0.00)
- Winter Park (p-value = 0.15)
<br>
<br>

Since Age, BMI, Smoker, and Winter Park values are the only ones that tested significant at 80%, we should look at the impact of their coefficients.

If a person’s Age increases by 1, Charges are expected to increase by $295.68, give or take $96.35. 

If a person’s BMI increases by 1, Charges are expected to increase by $392.64, give or take $242.51. 

If a person is a Smoker, Charges are expected to increase by $21,374.71, give or take $3,521.65.

If a person lives in Winter Park, Charges are expected to decrease by $4,358.32, give or take $3,787.84.
</font>

## Question 3

### Insurance Prediction 

<font face = Helvetica size = 2 color = black > The insurance agent returns with another client:<br>- Age: 35<br>- BMI: 26<br>- Children: 1<br>- Gender: Female<br>- Smoker: No<br>- City: Sanford<br><br>Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)</font>

---

```{r q3, echo=FALSE}
 newPrediction <- data.frame(Age = 35, BMI = 26, Children = 1, Female = 1, Smoker = 0, WinterSprings = 0, WinterPark = 0, Oviedo = 0)
predict (model, newdata = newPrediction, interval = "confidence", level = .95)

```
<font face = Helvetica size = 2 color = DarkSlateBlue > 
As per our regression equation, this Florida health insurance company can expect charges for this individual to annually be $9,517.64. However with a 95% confidence interval the lower bound of charges accumulated would be $5,868.46 to $13,166.82 annually.</font>

## Question 4

### Partial F-Test

<font face = Helvetica size = 2 color = black >Compare the model from question 1, to a model that does not include the group of city dummies. Does including the cities reduce the SSE by a statistically significant amount? (check the partial F-test for significance of the dummies as a group). Use $\alpha = 0.05$
</font>
---

#### Full Model
```{r q4, echo=FALSE}

model_full <- lm(Charges ~., data = insurance)

summary(model_full)
```

#### Reduced Model
```{r q4.1, echo=FALSE}

cities <- read_xlsx("../Data/insurance_0126_Group5.xlsx")

reduced_sat <- cities[,-(7:9)]

model_reduced <- lm(Charges ~. , data = reduced_sat)

summary(model_reduced)
```

#### Model Comparison
```{r q4.3, echo=FALSE}
anova(model_reduced, model_full)
```

<font face = Helvetica size = 2 color = DarkSlateBlue > 
Including the cities did not reduce the SSE by a statistically significant amount, but independently, both tested statistically significant.

<br>
<br>
The alpha value of 0.05 is not smaller than the p value 0.4748 between the two models. This result prevents us from successfully rejecting the null hypothesis. As a result, we lack sufficient data to draw the conclusion that the city factors are statistically significant to the fit of the model.
</font>
